\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym, fullpage, titlesec, marvosym, color, enumitem, hyperref, fancyhdr, babel, tabularx, multicol}
\usepackage[T1]{fontenc}
\usepackage{baskervillef}

% Margins Optimization
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{0.6in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Section Formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\color{black}\titlerule]

% Custom Commands
\newcommand{\resumeEntry}[4]{
  \item\textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}
}

\newcommand{\resumeDescription}[1]{
  \vspace{-2pt}\begin{itemize}[leftmargin=0.2in]
    #1
  \end{itemize}
}

\begin{document}

% Header
\begin{center}
    {\LARGE Pietro Gazzi}\\
        \begin{multicols}{2}
        \begin{flushleft}
            \textbf{Paris, 75011}\\
            \href{https://pietrowei.github.io/Portfolio}{\underline{\textcolor{blue}{My Portfolio}}}
        \end{flushleft}
        \begin{flushright}
            \href{mailto:pietrogazzi01@gmail.com}{pietrogazzi01@gmail.com}\\
            +33 0766968051
        \end{flushright}
    \end{multicols}
\end{center}

% Professional Summary
\section*{Professional Summary}\vspace{-5pt}
Data-driven professional with expertise in SQL, Python, and visualization tools (Power BI, Tableau). Experienced in predictive modeling, business process optimization, and strategic decision-making. Visit my \href{https://pietrowei.github.io/Portfolio}{\underline{\textcolor{blue}{portfolio}}} for more details.
% Work Experience
\section*{Work Experience}\vspace{-5pt}
\begin{itemize}[leftmargin=0.2in]
    \resumeEntry{Maintenance Analyst}{Leonardo Helicopters, Milan}{May 2024 -- Present}{}
    \resumeDescription{
        \item Analyzed and repaired structural components using data-driven methodologies.
        \item Developed SQL-based dashboards in Power BI, reducing repair turnaround time by 15\% and \\ increasing operational efficiency.
        \item Utilized statistical analysis and machine learning techniques to identify failure patterns.
        \item Collaborated with cross-functional teams to improve data collection and reporting processes.
        \item Conducted market analysis to identify business opportunities and optimize repair services.
    }
    \resumeEntry{Research Engineer}{Institut Polytechnique de Paris, Paris}{Feb 2023 -- May 2024}{}
    \resumeDescription{
        \item Analyze experimentally and numerically the crack propagation in 3D printed Polycarbonate and the \\ additive manufacturing of optimized specimens.ns.
        \item Performed data analysis to support research projects and improve experimental designs.
    }
    \resumeEntry{Structural Analyst}{Thales Alenia Space, Turin}{May 2022 -- Jan 2023}{}
    \resumeDescription{
        \item Developed data-driven models to predict structural performance and optimize designs.
        \item Analyzed structural cost-performance trade-offs using Python (Pandas, NumPy), optimizing component design and reducing production costs by 5\%
    }
\end{itemize}

% Education
\section*{Education}\vspace{-5pt}
\begin{itemize}[leftmargin=0.2in]
    \resumeEntry{Politecnico di Milano}{Aerospace Engineering}{Sept 2020 -- Dec 2022}{}
    \resumeEntry{Università degli Studi di Firenze}{Mechanical Engineering}{Sept 2017 -- Jul 2020}{}
    \resumeEntry{Coursera Certifications}{}{2024-2025}{}
\end{itemize}
\begin{multicols}{2}
    \small
    \begin{itemize}[leftmargin=0.4 in, label={-}]
        \item Investment Management with Python and Machine Learning (EDHEC)
        \item Google Data Analytics Professional Certificate (Google)
    \end{itemize}
    \begin{itemize}[leftmargin=0.3 in, label={-}]
        \item Data Science Specialization (Johns Hopkins University)
        \item PostgreSQL for Everybody (University of Michigan)
    \end{itemize}
\end{multicols}

% Specialized Skills
\section*{Specialized Skills}\vspace{-15pt}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Data Processing:} Data Cleaning, ETL, Data Wrangling
    \item \textbf{Business Intelligence:} Power BI, Tableau, Excel (Advanced)
    \item \textbf{Programming:} SQL (PostgreSQL, MySQL), Python (Pandas, NumPy, Matplotlib, Seaborn), LaTeX, HTML, CSS
    \item \textbf{Statistical Analysis:} A/B Testing, Regression Analysis, Business Metrics, Time Series Forecasting
\end{itemize}
\end{multicols}

% Languages
\section*{Languages}\vspace{- 5 pt}
\textbf{Italian:} Native \hspace{20pt} \textbf{English:} Fluent \hspace{20pt} \textbf{French:} Fluent \hspace{20pt} \textbf{German:} Beginner

\end{document}
