% !TEX TS-program = latexmk
\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\begin{document}

\begin{letter}{Hiring Team \
Too Good To Go \
Paris Office}

\opening{Dear Hiring Team,}

I am writing to express my strong interest in the Product Analyst position on the Retail Technologies team at Too Good To Go. As a data-driven professional with over three years of experience in B2B analytics, experiment design, and automation, I am excited by TGTG’s mission to fight food waste and create tangible impact through innovative software.

In my current role at Leonardo Helicopters, I partner with product and operations teams to define key performance metrics, design A/B tests for predictive maintenance features, and build real-time dashboards that reduced repair turnaround time by 15%. I automated data flows with Python and Airflow, cutting manual reporting effort by eight hours per week. These experiences honed my ability to translate complex data into actionable insights—a skill I am eager to apply at Too Good To Go to help retailers track, prioritize, and redistribute surplus food.

At Institut Polytechnique de Paris, I developed Python tooling to instrument process variables in additive manufacturing experiments, enabling automated anomaly detection and time-series forecasting. I collaborated cross-functionally to prototype decision‑support concepts, presenting results to senior stakeholders. This background in experiment set-up, feature instrumentation (Amplitude, Mixpanel), and BI platforms (Looker, Power BI) aligns directly with the responsibilities of driving product strategy and experimentation at TGTG.

What excites me most about Too Good To Go is the scale and social impact of the Retail Technologies platform: empowering tens of thousands of store employees to reduce waste, with a roadmap to reach hundreds of thousands by year’s end. I thrive in autonomous, values-driven environments, and I share your commitment to #oneteam collaboration, simplicity, and raising the bar. I am confident that my analytical rigor, technical curiosity, and passion for sustainable business will deliver measurable value to your Retail Partners and support TGTG’s growth.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills in SQL, Python, experimentation, and dashboarding can contribute to Too Good To Go’s mission. Please find my résumé and portfolio link attached.

\closing{Sincerely,}

Pietro Gazzi\
Paris, France\
\href{mailto:pietrogazzi01@gmail.com}{pietrogazzi01@gmail.com} | +33 0766968051

\end{letter}
\end{document}

